Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-07 writeup/gz_hubble_data.tex
Fixed error in task labeling. Closes #65.
Initial stab at ordering author list.

%% Authors with the same affiliation can be grouped in a single
%% \author and \affil call.
\author{Kyle W. Willett\altaffilmark{1,2}, Melanie A. Galloway\altaffilmark{1}, Chris J. Lintott\altaffilmark{3}, B.D. Simmons\altaffilmark{3,4,5,6}, Karen L. Masters\altaffilmark{7,8}, Tom Melvin\altaffilmark{7}, Steven P. Bamford\altaffilmark{9}, Edward M. Edmondson\altaffilmark{7}, Lucy F. Fortson\altaffilmark{1}, Kevin Schawinski\altaffilmark{10}, Edmond Cheung\altaffilmark{11}, Claudia Scarlata\altaffilmark{1}, Melanie Beck\altaffilmark{1}, Arfon M. Smith\altaffilmark{3,12,13}, Michael Parrish\altaffilmark{12}, Roger L. Griffith\altaffilmark{14,15}, Anna Han\altaffilmark{16}
}
%
% List of people who have contributed (not sure if everyone will be author)
% Definitely: Lintott, Bamford, Edmondson, Masters, Simmons, Melvin, Willett, Galloway, Fortson, Schawinski, Cheung
% Others on GZ science team: Urry, Cardamone, Nichol, Kaviraj, Keel, Skibba, Thomas, Wong, Scarlata, Beck, Smethurst
% Tech: Smith, Parrish, Simpson, other devs?
% External: Han, Griffith
%
%$^1$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
%$^2$South East Physics Network, www.sepnet.ac.uk\\
%$^3$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
%$^2$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
%$^4$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
%$^5$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
%$^6$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
%$^4$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
%$^7$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
%$^6$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
%$^7$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
%$^8$Einstein Fellow\\

@@

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH) project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image. Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$. The galaxies selected for GZH classifications go down to magnitude limits of $m_{I}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry. This paper also describes and employs a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline. This paper presents both the raw and calibrated morphological vote fractions for $150,771$ galaxies, constituting a large data set suitable for large-scale studies of galaxy evolution.

@@

The advent of larger telescopes in an increasing range of observable wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day. This occurs in a variety of pathways, including accretion of baryons from large-scale galactic filaments onto halos via streaming, mergers of individual dark matter halos along with their baryons, conversion of gas into stars via gravitational collapse and star formation, etc. The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes. Each of these processes affects on the galaxy morphology, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics involved \citep[for a recent review see][]{con14}.

@@

One of the major difficulties in studying the morphologies of galaxies in large samples lies in the system of measurement. Visual classification by experts has been used for many years \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}. These methods have advantages in using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration. Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts. The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images. With $>2\times10^5$~classifiers, this allows for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible. While the crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

This paper presents the results from the Galaxy Zoo Hubble (GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}. GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble.

The sample selection and creation of the images used for GZH is described in Section~\ref{sec:data}. Section~\ref{sec:interface} describes the GZH interface and the collection of classifications. Section~\ref{sec:debiasing} outlines the process used to calibrate and ``debias'' the crowdsourced votes. Section~\ref{sec:results} gives the main results as a catalog, with several examples of how the data may be queried in Section~\ref{sec:cookbook}. Section~\ref{sec:analysis} gives a short overview of the observed morphological demographics and compares them to several other catalogs, with a summary in Section~\ref{sec:summary}.

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in Galaxy Zoo: Hubble. The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope which were used to create color gradients in the composite images for COSMOS.\label{fig:filtercurves}}
\end{figure*}

@@

Single-epoch images from SDSS Stripe~82 were selected using the same criteria from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ > 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. 21,522 galaxies in SDSS met these criteria. Coadded images from Stripe~82 were selected from the union of galaxies with coadded magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a coadd source. This resulted in a larger set of 30,339 images. Of the images in the coadded sample, 5144 (17~percent) are dimmer than the initial magnitude cut of 17.77.

@@

The majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only one or two filters available when the GZH project was first launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo impossible. For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band was mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two. Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).

@@

Redshifts for the GZH catalog are compiled from a variety of sources. For each galaxy, the primary redshift used for debiasing calculations (Section~\ref{sec:debiasing}) is in the $\tt Z\_Best$ column of Table~\ref{tbl:catalog_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog of the redshift is included as $\tt Z\_BEST\_SOURCE$.

For galaxies which have published redshifts from multiple sources, the following algorithm is used to select the $\tt Z\_BEST$ quantity. This first priority is spectroscopic redshifts; these are provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A high quality spectroscopic redshift in the ACS-GC is the primary option; if none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in 3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more than 98\% are consistent at $\Delta z<0.001$, and so the order of selection makes no practical difference. If no spectroscopic redshifts are available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data are used to select the redshift with the smallest error. Table~\ref{tbl:redshifts} shows the results of this selection.

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{l|rr|rrr|rr|r|rr}
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{GZH redshifts by survey\label{tbl:redshifts}} 
\tabletypesize{\scriptsize}
\tablehead{
 &   
\multicolumn{2}{c}{\underline{ACS-GC}} &
\multicolumn{3}{c}{\underline{3DHST}} &
\multicolumn{2}{c}{\underline{MUSYC}} &
\multicolumn{1}{c}{\underline{UltraVISTA}}&
\multicolumn{2}{c}{\underline{Total}} 
\\
\colhead{Survey} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{grism-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{photo-z} & 
\colhead{with redshift} &
\colhead{in survey}
}
\small
\startdata
%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020 & 92,808 \\
GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328  & 12,030 \\
GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040  & 10,284 \\
SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545 & 51,861  \\
\hline
Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
\enddata
\end{deluxetable*}

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{Flowchart of the questions presented to GZH users, labeled with the corresponding Task numbers. Tasks in the decision tree are color-coded by tier level: Gray-colored Tasks are 1st tier questions which are asked of all users. Tasks colored green, blue, purple, and pink (respectively) are one, two, three, or four steps below branching points in the decision tree.}
\label{fig:decisiontree}
\end{figure*}

\subsection{User weighting}\label{ssec:weighting}
The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree. Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The user weighting $w$ is 1 for the top 95\% of users as ranked by consistency. For the bottom 5\% of users, $w$ drops smoothly and is effectively zero for only the bottom 1\% of classifiers in the CDF. The overall effect on the GZH dataset is relatively small, but this method is effective at filtering out contributions from random or delibrately malicious classifiers.

@@

\subsection{Selection of FERENGI input galaxies}

@@

%The selection criteria for the different morphological categories is summarized in Table \ref{tbl:morphologies}. 
The surface brightness selection ($N_\mu = 3$) for the FERENGI galaxies was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts'' ($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.

>>>>

%% Authors with the same affiliation can be grouped in a single
%% \author and \affil call.
\author{Kyle W. Willett\altaffilmark{1,2}, Melanie A. Galloway\altaffilmark{1}, Karen L. Masters\altaffilmark{3,4}, B.D. Simmons\altaffilmark{5,6,7}, Chris J. Lintott\altaffilmark{5}, Steven P. Bamford\altaffilmark{8}, Edmond Cheung\altaffilmark{9}, Tom Melvin\altaffilmark{3}, Lucy F. Fortson\altaffilmark{1}, Melanie Beck\altaffilmark{1}, Claudia Scarlata\altaffilmark{1}, Roger L. Griffith\altaffilmark{10,11}, Kevin Schawinski\altaffilmark{12}, Edward M. Edmondson\altaffilmark{3}, Arfon M. Smith\altaffilmark{5,13,14}, Michael Parrish\altaffilmark{13}, Anna Han\altaffilmark{15}
}
%
%$^N$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
%$^N$South East Physics Network, www.sepnet.ac.uk\\
%$^N$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
%$^N$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
%$^N$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
%$^N$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
%$^N$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
%$^N$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
%$^N$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
%$^N$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
%$^N$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
%$^N$Einstein Fellow\\

@@

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH) project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image. Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$. The galaxies selected for GZH classifications go down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry. This paper also describes and employs a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline. The GZH catalog includes both the raw and calibrated morphological vote fractions for $150,771$ galaxies, constituting a large data set suitable for large-scale studies of galaxy evolution.

@@

The advent of larger telescopes in an increasing range of observable wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day. This occurs in a variety of pathways, including accretion of baryons from large-scale galactic filaments onto halos via streaming, mergers of individual dark matter halos along with their baryons, conversion of gas into stars via gravitational collapse and star formation, etc. The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes. Each of these processes affects the galaxy morphology in different ways, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics involved \citep[for a recent review see][]{con14}.

@@

One of the major difficulties in studying the morphologies of galaxies in large samples lies in the system of measurement. Visual classification by experts has been used for many years \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}. These methods have advantages in using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration. Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts. The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images. The efforts of more than $2\times10^5$~classifiers allow for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible. While the crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

This paper presents the results from the Galaxy Zoo Hubble (GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}. GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble. The Galaxy Zoo: CANDELS project also classified morphologies of galaxies at high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).

The sample selection and creation of the images used for GZH is described in Section~\ref{sec:data}. Section~\ref{sec:interface} describes the GZH interface and the collection of classifications. Section~\ref{sec:debiasing} outlines the process used to calibrate and correct the crowdsourced vote fractions for redshift-dependent bias. Section~\ref{sec:results} gives the main catalog of results, with several examples of how the data may be queried in Section~\ref{sec:cookbook}. Section~\ref{sec:analysis} gives a short overview of the observed morphological demographics and compares them to several other catalogs, with a summary in Section~\ref{sec:summary}.

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in GZH. The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope, which was used to create color gradients in the GZH images for COSMOS.\label{fig:filtercurves}}
\end{figure*}

@@

Single-epoch images from SDSS Stripe~82 were selected using the same criteria from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ > 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The images used are three-color composites using the $g^\prime$, $r^\prime$, and $i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria. Coadded images from Stripe~82 were selected from the union of galaxies with coadded magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a coadd source. This resulted in a larger set of 30,339 images. Of the images in the coadded sample, 5144 (17~percent) are dimmer than the initial magnitude cut of 17.77.

@@

The majority of the data in Legacy surveys described in Section~\ref{ssec:legacy_surveys} had images in only one or two filters available when the GZH project was first launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo impossible. For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band was mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two. Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).

@@

Redshifts for the GZH catalog are compiled from a variety of sources. For each galaxy, the primary redshift used for debiasing calculations (Section~\ref{sec:debiasing}) is in the $\tt Z\_BEST$ column of Table~\ref{tbl:catalog_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog of the redshift is included as $\tt Z\_BEST\_SOURCE$.

For galaxies which have published redshifts from multiple sources, the following algorithm is used to select the $\tt Z\_BEST$ quantity. This first priority is spectroscopic redshifts; these are provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A high quality spectroscopic redshift in the ACS-GC is the primary option; if none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in 3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more than 98\% are consistent at $\Delta z<0.001$, and so the order of selection makes no practical difference. If no spectroscopic redshifts are available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data are used to select the redshift with the smallest error. %Table~\ref{tbl:redshifts} shows the results of this selection.

@@

%\tabletypesize{\scriptsize}
%\begin{deluxetable*}{l|rr|rrr|rr|r|rr}
%\tablecolumns{12}
%\tablewidth{0pc}
%\tablecaption{GZH redshifts by survey\label{tbl:redshifts}} 
%\tabletypesize{\scriptsize}
%\tablehead{
% &   
%\multicolumn{2}{c}{\underline{ACS-GC}} &
%\multicolumn{3}{c}{\underline{3DHST}} &
%\multicolumn{2}{c}{\underline{MUSYC}} &
%\multicolumn{1}{c}{\underline{UltraVISTA}}&
%\multicolumn{2}{c}{\underline{Total}} 
%\\
%\colhead{Survey} & 
%\colhead{spec-z} & 
%\colhead{photo-z} & 
%\colhead{spec-z} & 
%\colhead{grism-z} & 
%\colhead{photo-z} & 
%\colhead{spec-z} & 
%\colhead{photo-z} & 
%\colhead{photo-z} & 
%\colhead{with redshift} &
%\colhead{in survey}
%}
%\small
%\startdata
%%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
%AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
%COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020 & 92,808 \\
%GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
%GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328  & 12,030 \\
%GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040  & 10,284 \\
%SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545 & 51,861  \\
%\hline
%Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
%\enddata
%\end{deluxetable*}

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{Flowchart of the questions presented to GZH users, labeled with the corresponding Task numbers. Tasks in the decision tree are color-coded by tier level: Gray-colored Tasks are 1$^\mathrm{st}$-tier questions which are asked of all users. Tasks colored green, blue, purple, and pink (respectively) are one, two, three, or four steps below branching points in the decision tree.}
\label{fig:decisiontree}
\end{figure*}

\subsection{User weighting}\label{ssec:weighting}
The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree. Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The user weighting $(w)$ is 1 for the top 95\% of users as ranked by consistency. For the bottom 5\% of users, $w$ drops smoothly and is effectively zero for only the bottom 1\% of classifiers in the CDF. Since this only affects a tiny percentage of the users (and an even smaller percentage of the classifications) the overall effect on the GZH dataset is minimal. This method is primarily effective, however, at filtering out contributions from random or delibrately malicious classifiers.

@@

\subsection{Selection of \ferengi{} input galaxies}

@@

%The selection criteria for the different morphological categories is summarized in Table \ref{tbl:morphologies}. 
The surface brightness selection ($N_\mu = 3$) for the \ferengi{} galaxies was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts'' ($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.

%\begin{table*}
%\center
%\caption{Summary of morphological categories selected for \ferengi{} sample.\label{tbl:morphologies}}
%\begin{tabular}{lllc}
%\hline\hline
%Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
%                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
%\hline
%Features            & Yes       & $p_{\rm features} > 0.8$, $p_{\rm odd} < 0.1$                                                         & 12 \\ 
%                    & Int.      & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$                                                     & 12 \\ 
%                    & No        & $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$                                                           & 12 \\ 
%Merger              & No        & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$                                 & 12 \\
%                    & Int.      & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
%                    & Yes       & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$                                                           & 12 \\
%Edge-on             & Yes       & $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$                                                      & 12 \\
%                    & Int.      & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$                                               & 12 \\
%                    & No        & $p_{\rm edgeon} < 0.2$, $p_{\rm features} > 0.5$                                                      & 12 \\
%Bar                 & No        & $p_{\rm bar} < 0.1$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
%                    & Int.      & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
%                    & Yes       & $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
%Visible spiral      & No        & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
%                    & Int.      & $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$   & 12 \\
%                    & Yes       & $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
%Oblique bulge size  & No        & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$          & 12 \\
%                    & Int.      & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
%                    & Yes       & $p_{\rm obvious|dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
%Edge-on bulge shape & Round     & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
%                    & Boxy      & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$                                  & 12 \\
%                    & No bulge  & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
%\hline\hline
%\end{tabular}
%\end{table*}
